\documentclass[12pt,sans]{moderncv}

% moderncv themes
\moderncvstyle{classic}
\moderncvcolor{green}

\usepackage[a4paper, hmargin=1in, vmargin=1in]{geometry}
\usepackage[a-2u]{pdfx}
\usepackage[czech]{babel}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{textcomp}

% personal data
\name{\mbox{Jakub}}{\mbox{Klener}}
\title{Curriculum vit\ae{}}
\address{Eliášova 460/35}{160 00, Praha 6 -- Bubeneč}
\phone[mobile]{722\,411\,643}
\email{jakub.v.klener@gmail.com}
\homepage{fu.mff.cuni.cz/biomolecules/Klener\_Jakub/}
\date{15. prosince 2021}
\begin{document}

\recipient{~}{}
\opening{~}

\makelettertitle


\section{Seznam publikací}

\noindent

\begin{enumerate}
\setlength\itemsep{3mm}

\item
KLENER, Jakub; HOFBAUEROVÁ, Kateřina; BARTOŠ, Aleš; ŘÍČNÝ, Jan; ŘÍPOVÁ,
Daniela; KOPECKÝ, Vladimír, Jr.,
2014.
Instability of cerebrospinal fluid after delayed storage and repeated freezing:
a holistic study by drop coating deposition Raman spectroscopy.
\emph{Clinical Chemistry and Laboratory Medicine}.
52(5), 657 -- 664.

\item
KLENER, Jakub; ŠTĚPÁNEK, Josef,
2015.
UV resonance Raman study of PolyA and PolyU complexes: Mg$2+$-induced formation
of PolyU$\cdot$polyA$\cdot$PolyU triplexes.
\emph{Vibrational Spectroscopy}.
81(5), 32 -- 39.

\item
KLENER, Jakub; ŠTĚPÁNEK, Josef,
2021.
Full UV resonance Raman analysis of temperature effects on the structural
arrangement of DNA segments.
\emph{Journal of Raman Spectroscopy}.
52(3), 678 -- 689.
\end{enumerate}


\section{Prezentace na mezinárodních konferencích}

\begin{enumerate}
\setlength\itemsep{3mm}

\item
KLENER, Jakub; HOFBAUEROVÁ, Kateřina; BARTOŠ, Aleš; ŘÍPOVÁ, Daniela;
KOPECKÝ, Vladimír, Jr.,
2012
Drop coating deposition Raman spectroscopy as the diagnostic tool of Alzheimer
disease.
\emph{XXIII. ICORS}. Bangalore, India.

\item
KLENER, Jakub; ŠTĚPÁNEK, Josef,
2013.
UV Resonance Raman of Adenine Containing NA Constituents: Effect of Molecular
Composition and Environmental Conditions.
\emph{Seventh International Conference on Advanced Vibrational Spectroscopy}.
Kobe, Japan.

\item
KLENER, Jakub; ŠTĚPÁNEK, Josef,
2014.
UV Resonance Raman Study of Mg$^2+$-induced formation of polyU·polyA·polyU
triplexes.
\emph{XXIV. ICORS}.
Jena, Germany.

\item
LINDNEROVÁ-MUDROŇOVÁ, Kateřina; MOJZEŠ, Peter; KLENER, Jakub; HOFBAUEROVÁ,
Kateřina; KOPECKÝ, Vladimír; BEDNÁROVÁ, Lucie,
2016.
Interquadruplex transitions of human telomeric sequences in K$^+$ solutions
under molecular crowding conditions and sub-melting temperatures.
\emph{EUCMOS}.
Szeged, Hungary.

\end{enumerate}


\end{document}
